### 2022-06-07 main/chapter_2ljets.tex
remove subsub; rearrange figure locations; minor fixes

@@

The high regions, defined in Table~\ref{tab:2ljets_high}, comprise SR-High,
SR-High-1J, and SR-$\llbb$.
To maximize projected sensitivity, SR-High is split into four bins with
splits at $\rjj = 0.8$, to form SR-High-8 and SR-High-16, and second at
$\metsig = 21$ to split these into SR-High-*-a and SR-High-*-b.
For example, SR-High-8-b requires $\rjj < 0.8$ and $\metsig > 21$.
The regions SR-High-8 and SR-High-16 are displayed in
Figure~\ref{fig:2ljets_high_region}, with their -a and -b bins visible across
the $\metsig$ distribution.

@@

\subsubsection{High}

\subsubsection{Mono-jet}

\subsubsection{\texorpdfstring{$\llbb$}{\textit{llbb}}}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_prepre_met_Sign_VRpresel_2j_MCfakeslogY.pdf}
\caption{$\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_prepre_mt2leplsp_0_VRpresel_2j_MCfakeslogY.pdf}
\caption{$\mttwoll$}
\end{subfigure}
\caption[
Histograms in a very loose pre-selection like those inspected to validate
background modelling prior to designing the $\twoljets$ regions.
]{%
Histograms in a very loose pre-selection like those inspected to validate
background modelling prior to designing the $\twoljets$ regions.
This selection requires `Pre-selection' from Table~\ref{tab:2ljets_presel} and
$\njet \geq 2$.
Errors are statistical.
Each last bin contains overflow.
}
\label{fig:2ljets_prepre}
\end{figure}

>>>>

The high regions, defined in Table~\ref{tab:2ljets_high}, comprise SR-High,
SR-High-1J, and SR-$\llbb$.

@@

To maximize projected sensitivity, SR-High is split into four bins with
splits at $\rjj = 0.8$, to form SR-High-8 and SR-High-16, and second at
$\metsig = 21$ to split these into SR-High-*-a and SR-High-*-b.
For example, SR-High-8-b requires $\rjj < 0.8$ and $\metsig > 21$.
The regions SR-High-8 and SR-High-16 are displayed in
Figure~\ref{fig:2ljets_high_region}, with their -a and -b bins visible across
the $\metsig$ distribution.

@@

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_prepre_met_Sign_VRpresel_2j_MCfakeslogY.pdf}
\caption{$\metsig$}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_prepre_mt2leplsp_0_VRpresel_2j_MCfakeslogY.pdf}
\caption{$\mttwoll$}
\end{subfigure}
\caption[
Histograms in a very loose pre-selection
]{%
Histograms in a very loose pre-selection like those inspected to validate
background modelling prior to designing the $\twoljets$ regions.
This selection requires `Pre-selection' from Table~\ref{tab:2ljets_presel} and
$\njet \geq 2$.
Errors are statistical.
Each last bin contains overflow.
}
\label{fig:2ljets_prepre}
\end{figure}
